Convergent Evolution During Local Adaptation to Patchy Landscapes

### 2014-07-05 patchy-selection-paper.tex
added refs for standinf paper

The convergent evolution of similar phenotypes 
in response to shared selection pressures is a testiment to the power of selection 
to repeatedly sculpt phenotypic variation. 
In some cases this convergence extends to the molecular level, 
with disparate taxa converging to the same phenotype through parallel 
genetic changes in the same pathway, genes, 
or even by precisely the same genetic changes
\citep{stern2013genetic,zhen2012parallel,martin2013repeated}. 
Convergent adaptation can also occur within species, if individuals within a species 
adapt to the same environment, in parallel, through different genetics changes. 
There are a growing number of examples of this in a range of well studied organisms and phenotypes \citep{Arendt:08}.
Such evolution of convergent phenotypes is favored by higher mutational input, 
i.e.\ larger mutational target and/or population size \citep{softsweepsII}.
The geographic distribution of populations can also affect the probability of parallel mutation within a species:
a widespread species is more likely to adapt by multiple, parallel mutations if dispersal is geographically limited, 
since subpopulations will adapt via new mutations before the adaptive allele arrives via migration \citep{ralph2010parallel}. 
Standing variation for a trait can also increase the probability of convergence, 
as standing variation for an allele increases the probability that the selective sweep will be \emph{soft}
(beginning from a base of multiple copies),
leading to genetic patterns similar to convergent adaptation \citep{orr2001sieve,softsweepsI}.

>>>>

The convergent evolution of similar phenotypes 
in response to shared selection pressures is a testament to the power of selection 
to repeatedly sculpt phenotypic variation. 
In some cases this convergence extends to the molecular level, 
with disparate taxa converging to the same phenotype through parallel 
genetic changes in the same pathway, genes, 
or even by precisely the same genetic changes
\citep{stern2013genetic,zhen2012parallel,martin2013repeated}. 
Convergent adaptation can also occur within species, if individuals within a species 
adapt to the same environment, in parallel, through different genetics changes. 
There are a growing number of examples of this in a range of well studied organisms and phenotypes \citep{Arendt:08}.
Such evolution of convergent phenotypes is favored by higher mutational input, 
i.e.\ larger mutational target and/or population size \citep{softsweepsII}.
The geographic distribution of populations can also affect the probability of parallel mutation within a species:
a widespread species is more likely to adapt by multiple, parallel mutations if dispersal is geographically limited, 
since subpopulations will adapt via new mutations before the adaptive allele arrives via migration \citep{ralph2010parallel}. 
Standing variation for a trait can also increase the probability of convergence, 
as standing variation for an allele increases the probability that the selective sweep will be \emph{soft}
(beginning from a base of multiple copies),
leading to genetic patterns similar to convergent adaptation \citep{orr2001sieve,softsweepsI}.

### 2014-07-05 standing-variation-paper.tex
added refs for standinf paper

@@

>>>>

\paragraph{}
So we can put these ingredients together for a simple model of the
geographic spread of alleles. A cartoon example of this process is
shown in Figure \ref{fig:cartoon} Initially, when the selection
pressures change at $t=0$, a set of standing variants can start to
spread having escaped loss through drift. These variants are shown as
little lightning bolts, and occur at a density $\lambda_0$ across
space. 
They spread at velocity $v$ carving out cones in space-time. As these
alleles proceed in their geographic spread other new alleles can arise
and become established in parallel, these are shown as little
stars. These new mutations arise and become established at rate $\lambda$.

@@

\paragraph{G6PD}
34 variants across 4; 000; 000 km2
15 common variants

515 codons

Selection coefficient (s) 	A- 0.044 (0.019–0.048)  Med	0.034
(0.014–0.049)  ``The mean age of the A− allele in these runs was 6357 years, with a 95\% credibility interval extending from 3840 to 11,760 years. For the Med alleles, the mean age was 3330 years with a 95\% credibility interval of 1600 to 6640 years"
\citet{tishkoff-g6pd}

s 0.24 and t= 40 generations \citep{Slatkin-age-est}

The estimated age is ~100 generations with an upper bound of <150
generations A- 0.1 < s < 0.2 \citep{Saunders-g6pd}

46 to 58\% reduction in risk of severe malaria for both female heterozygotes and male hemizygotes estimates of selection pressure \citep{Ruwende-g6pd}

Mahidol487A mutation started to increase at ~1500 YBP, with a
selection intensity of ~0.23 \citep{Louicharoen-g6pd}
Show's effect in het and homozy females
